Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-12 doc/manuscript/manuscript.Rmd
rerun manuscript

>>>>

In this study, we characterized the diversity of *Sclerotinia sclerotiorum* from dry bean fields across the United States.
Our results suggest that populations from white mold nurseries may reflect the populations of the surrounding regions. 
We found significant population differentiation by geographic region, mainly differentiated into four broad groups, a Coastal Region, Midwestern Region, International Region, and Mexico. 
There were not significant associations between multilocus genotypes and mycelial compatibility groups.
